Assessing MCR Discussion Usefulness using Semantic Similarity

### 2014-07-29 sections/discussion.tex
updated graph to include legend

%\subsection{Binary Classification}
\subsection{How much impact of unclear class on model construction?}
Another approach we tried is to perform a \emph{binary classification}.
This means we assume that there are no unclear or undetermined comments; only useful and useless.
For this, we removed the samples with 1 and 2 \texttt{YES} votes from our data set. 209 samples without disagreements are left.
By performing cross-validation using only samples with 0 and 3 \texttt{YES} votes, we obtained a much better F$_1$ score of 0.896.

We could not objectively measure the F$_1$ score for all samples, because giving positive or negative classification to 1 and 2-scored samples introduces a bias.
However, the results seen in Fig.\ref{fig:binary} suggests that the binary classifier tends to gives positive classification to samples with score of 2 more than samples with score of 1, and the \emph{vice versa} for negative classification.

>>>>

%\subsection{Binary Classification}
\subsection{How much impact of unclear class on model construction?}
Another approach we tried is to perform a \emph{binary classification}.
This means we assume that there are no unclear or undetermined comments; only useful and useless.
For this, we removed the samples with 1 and 2 \texttt{YES} votes from our training set.
This leaves us with 209 remaining samples, all without a disagreement.
By performing cross-validation using these samples, we obtained a much better F$_1$ score of 0.896.

However, we could not objectively measure the F$_1$ score for all samples, because giving positive or negative classification to 1 and 2-scored samples introduces a bias.
But interestingly, the results seen in Fig.\ref{fig:binary} suggests that the binary classifier tends to gives positive classification to samples with score of 2 more than samples with score of 1, and the \emph{vice versa} for negative classification.
